Title

### 2013-03-19 inc/hardware/column.tex
added some content, but also restructured some of the folders related to hardware

The vacuum chamber itself is almost entirely 4.5 in standard ConFlat hardware.
Much has been purchased from off-the-shelf hardware suppliers.
More complicated chamber components have been purchased from Kimball Physics Inc.

@@

  \begin{figure}
    \centering
    \includegraphics{chamber.jpg}
    \caption[Side view of main chamber]{
      Assembled side view of the main chamber section of the UEM column at UIC.
      To the left are the high-voltage passthrough and ``port aligner'' to which the cathode is mounted.
      Visible inside the window are the cathode Wehnelt and photocathode (left), the side of the anode, and the side of the deflector plates assembly just after the anode (right).
      The anode and plate-assembly are mounted by the ``eV parts'' system attached to the main chamber.
      The wires and connectors supplying the voltage to the plates are also clearly visible.
    }
    \label{fig:chamber-pic}
  \end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics{chamber.jpg}
  \caption[Side view of main chamber]{
    Assembled side view of the main chamber section of the UEM column at UIC.
    To the left are the high-voltage passthrough and ``port aligner'' to which the cathode is mounted.
    Visible inside the window are the cathode Wehnelt and photocathode (left), the side of the anode, and the side of the deflector plates assembly just after the anode (right).
    The anode and plate-assembly are mounted by the ``eV Parts'' system attached to the main chamber.
    The wires and connectors supplying the voltage to the plates are also clearly visible.
  }
  \label{fig:chamber-pic}
\end{figure}

The vacuum chamber itself is almost entirely 4.5 in standard ConFlat hardware.
Much has been purchased from off-the-shelf hardware suppliers.
More complicated chamber components have been fabricated in-house or purchased from Kimball Physics Inc.

@@

### 2013-03-19 inc/hardware/magnetic_lenses/maglens.tex
added some content, but also restructured some of the folders related to hardware

\subsection{Motivation}
% montgomery_some_1961
% el-kareh_electron_1970

@@

Magnetic lenses present some challenges for Ultrafast Electron Microscopy.
First, the beams are likely to be much larger and thus a UEM will need large-aperture lenses.
Second, and more importantly, near a lens crossover (i.e. focus), the charge density can increase rapidly.
This charge density can lead to an unacceptable amount of space-charge interaction (see section \ref{sec:free_spacecharge}).

@@

Discussion of the mathematics of magnetic lenses can be found in Section \ref{sec:mag_lens}.
While in principle one could design a magnetic lens using \ref{eq:lens_eq_of_motion} and \ref{eq:field_of_loop}, the process wouldn't be very practical or instructive.
Further --- as suggested by the use of the $H$ field in \ref{eq:field_of_loop} --- better performance of the lens can be achieved by concentrating the field using materials with high magnetic permeablility.
These materials, called ``magnetic shielding'' since it captures the magnetic field lines, can direct the field lines to a small gap, known as the ``pole-piece gap''.
The field lines exit the shielding in the gap and it is this field that acts as the lens.
This gap can be much smaller than the total width of the coil turns, and yet contain in a field commensurate with the full coil.

>>>>

%\subsection{Motivation}
% montgomery_some_1961
% el-kareh_electron_1970

@@

Magnetic lenses present some challenges for Ultrafast Electron Microscopy.
First, the beams are likely to be much larger and thus a UEM will need large-aperture lenses.
Second, and more importantly, near a lens crossover (i.e. focus), the charge density can increase rapidly.
This charge density can lead to an unacceptable amount of space-charge interaction.
These effects have been explored in Sections \ref{sec:free_spacecharge} and \ref{sec:mag_lens_charge}.
The lenses I present in this section were designed, in part, using information computed by the extended AG model (Section \ref{sec:mag_lens_model}).

@@

Discussion of the mathematics of magnetic lenses can be found in Section \ref{sec:mag_lens}.
While in principle one could design a magnetic lens using \ref{eq:lens_eq_of_motion} and \ref{eq:field_of_loop}, the process wouldn't be very practical or instructive.
Further --- as suggested by the use of the auxiliary field $H$ field in \ref{eq:field_of_loop} --- better performance of the lens can be achieved by concentrating the field using materials with high magnetic permeablility.
These materials, called ``magnetic shielding'' since it captures the magnetic field lines, can direct the field lines to a small gap, known as the ``pole-piece gap''.
The field lines exit the shielding in the gap and it is this field that acts as the lens.
This gap can be much smaller than the total width of the coil turns, and yet contain in a field commensurate with the full coil.
